Model of lens candidates from Space Warps CFHTLS

### 2016-07-07 paper2.tex
editing

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1171M,2016MNRAS.455.1191M} have
between them discovered an average of four lenses per square degree.
So one can be optimistic about finding many thousands of lenses in the
next generation of wide-field surveys.  But modelling them all will be
very difficult if the process is labour-intensive.

\cite{2015MNRAS.447.2170K} developed a new lens-modelling strategy
developed, designed to be scaleable to much larger lens samples.  The
idea was to collaborate with experienced members of the
citizen-science community, who had already participated in lens
discovery through Space~Warps, as well as several other projects
involving astronomical data.  The

>>>>

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling modelling effort to
reconstruct their mass distributions.

To prepare for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through Space~Warps, as well as
several other projects involving astronomical data.  The style of
collaboration differs, however, from Space~Warps itself.  Space~Warps
works by sourcing a simple task to very large crowd

2016MNRAS.455.1171M,
